An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-23 paper.tex
Simply discussion of backward time travel

Representing evolving graphs as sparse matrices offers great flexibility
on the search direction. If we define the \emph{backward-neighbors} of a
node $(v,t)$ to be a set of nodes that precede $(v,t)$ if we travel backwards
in time. Then the backward-neighbors of $(v,t)$ can be computed by
\begin{equation}
\label{eq:backward}
(A^{[t]})b + (A^{[t+1]})\odot b + \cdots + (A^{[n]})\odot b.
\end{equation}
We shall get a backward traversal algorithm if we replace
the vector-matrix multiplication $\bm{A_n}^T\bm{b}$
by $\bm{A_n}\bm{b}$, where
\[
\bm{A_n} =
\begin{bmatrix}
A^{[1]} &   0            & \cdots  &  & 0 \\
\sigma(A^{[2]}) & A^{[2]} & 0         &\cdots  & \vdots \\
\sigma(A^{[3]}) & \sigma(A^{[3]}) & A^{[3]} & \cdots \\
   \vdots              &                              &      \vdots            &  &  \vdots \\
\sigma(A^{[n]}) &                  &       \cdots                      &  & A^{[n]}
\end{bmatrix}.
\]
Having the ability to traverse backwards is important for many real-life applications.
We shall show an example in Section \ref{sec:applications}.

@@

>>>>

@@

Tracing influence through citation networks naturally lead to considering paths
through evolving graphs that traverse time backwards. While we have until now
only considered forward evolution in time, the treatment for reverse evolution
follows naturally simply by reversing the time labels, e.g.\ by the transformation
$t\rightarrrow -t$.

% Representing evolving graphs as sparse matrices offers great flexibility
% on the search direction. If we define the \emph{backward-neighbors} of a
% node $(v,t)$ to be a set of nodes that precede $(v,t)$ if we travel backwards
% in time. Then the backward-neighbors of $(v,t)$ can be computed by
% \begin{equation}
% \label{eq:backward}
% (A^{[t]})b + (A^{[t+1]})\odot b + \cdots + (A^{[n]})\odot b.
% \end{equation}
% We shall get a backward traversal algorithm if we replace
% the vector-matrix multiplication $\bm{A_n}^T\bm{b}$
% by $\bm{A_n}\bm{b}$, where
% \[
% \bm{A_n} =
% \begin{bmatrix}
% A^{[1]} &   0            & \cdots  &  & 0 \\
% \sigma(A^{[2]}) & A^{[2]} & 0         &\cdots  & \vdots \\
% \sigma(A^{[3]}) & \sigma(A^{[3]}) & A^{[3]} & \cdots \\
%    \vdots              &                              &      \vdots            &  &  \vdots \\
% \sigma(A^{[n]}) &                  &       \cdots                      &  & A^{[n]}
% \end{bmatrix}.
% \]
% Having the ability to traverse backwards is important for many real-life applications.
% We shall show an example in Section \ref{sec:applications}.
